### 2018-03-26 submission/manuscript.Rmd
convert abstract to active voice

**Methods.** DNA from fecal samples (n=4) were extracted using a PowerMag DNA extraction kit with a 10 minute bead beating step and amplified at 15, 20, 25, 30, and 35 cycles using Accuprime, Kappa, Phusion, Platinum, or Q5 HiFi DNA polymerase. Mock communities (technical replicates n=4) consisting of previously isolated whole genomes of 8 different bacteria were also amplified using the same approach. The number of OTUs (Operational Taxonomic Units) were examined for both fecal samples and mock communities. Next, Bray-Curtis index, the error rate, sequence error prevalence, and chimera prevalence were investigated. Finally, the chimera prevalence correlation with number of OTUs was assessed.

**Results.** When analyzing fecal samples a different number of OTUs was observed between HiFi DNA polymerases at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001). These HiFi dependent differences in the number of OTUs were identified as early as 20 cycles in the mock communities (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`). Chimera prevalence varied by HiFi DNA polymerase and this variation was still present after chimera removal using VSEARCH. The chimera prevalence was positively correlated with the number of OTUs and was also not affected by chimera removal with VSEARCH.

>>>>

**Methods.** We extracted DNA from fecal samples (n=4) using a PowerMag DNA extraction kit with a 10 minute bead beating step and amplified at 15, 20, 25, 30, and 35 cycles using Accuprime, Kappa, Phusion, Platinum, or Q5 HiFi DNA polymerase. Amplification of mock communities (technical replicates n=4) consisting of previously isolated whole genomes of 8 different bacteria used the same approach. The analysis initially examined the number of Operational Taxonomic Units (OTUs) for both fecal samples and mock communities. It also assessed HiFi DNA polymerase dependent differences in the Bray-Curtis index, error rate, sequence error prevalence, and chimera prevalence. Finally, our analysis also examined chimera prevalence correlation with the number of OTUs.

**Results.** When analyzing fecal samples we observed a different number of OTUs between HiFi DNA polymerases at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001). Our analysis identified these HiFi dependent differences in the number of OTUs as early as 20 cycles in the mock communities (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`). Chimera prevalence varied by HiFi DNA polymerase and this variation persisted after chimera removal using VSEARCH. We also observed positive correlations between chimera prevalence and the number of OTUs which was not affected by chimera removal with VSEARCH.

### 2018-03-26 submission/manuscript.tex
convert abstract to active voice

\textbf{Methods.} DNA from fecal samples (n=4) were extracted using a
PowerMag DNA extraction kit with a 10 minute bead beating step and
amplified at 15, 20, 25, 30, and 35 cycles using Accuprime, Kappa,
Phusion, Platinum, or Q5 HiFi DNA polymerase. Mock communities
(technical replicates n=4) consisting of previously isolated whole
genomes of 8 different bacteria were also amplified using the same
approach. The number of OTUs (Operational Taxonomic Units) were examined
for both fecal samples and mock communities. Next, Bray-Curtis index,
the error rate, sequence error prevalence, and chimera prevalence were
investigated. Finally, the chimera prevalence correlation with number of
OTUs was assessed.

\textbf{Results.} When analyzing fecal samples a different number of
OTUs was observed between HiFi DNA polymerases at 35 cycles (P-value
\textless{} 0.0001). These HiFi dependent differences in the number of
OTUs were identified as early as 20 cycles in the mock communities
(P-value = 0.002). Chimera prevalence varied by HiFi DNA polymerase and
this variation was still present after chimera removal using VSEARCH.
The chimera prevalence was positively correlated with the number of OTUs
and was also not affected by chimera removal with VSEARCH.

>>>>

\textbf{Methods.} We extracted DNA from fecal samples (n=4) using a
PowerMag DNA extraction kit with a 10 minute bead beating step and
amplified at 15, 20, 25, 30, and 35 cycles using Accuprime, Kappa,
Phusion, Platinum, or Q5 HiFi DNA polymerase. Amplification of mock
communities (technical replicates n=4) consisting of previously isolated
whole genomes of 8 different bacteria used the same approach. The
analysis initially examined the number of Operational Taxonomic Units
(OTUs) for both fecal samples and mock communities. It also assessed
HiFi DNA polymerase dependent differences in the Bray-Curtis index,
error rate, sequence error prevalence, and chimera prevalence. Finally,
our analysis also examined chimera prevalence correlation with the
number of OTUs.

\textbf{Results.} When analyzing fecal samples we observed a different
number of OTUs between HiFi DNA polymerases at 35 cycles (P-value
\textless{} 0.0001). Our analysis identified these HiFi dependent
differences in the number of OTUs as early as 20 cycles in the mock
communities (P-value = 0.002). Chimera prevalence varied by HiFi DNA
polymerase and this variation persisted after chimera removal using
VSEARCH. We also observed positive correlations between chimera
prevalence and the number of OTUs which was not affected by chimera
removal with VSEARCH.
